\documentclass[10.5pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem} % "a, b, c" instead of "1, 2, 3" for dot points
\usepackage{fancyhdr}

% Footer
%% First page
\fancypagestyle{plain}{
    \fancyhf{} % Clear default header and footer
    \fancyfoot[L]{QFin UWA}
    \fancyfoot[C]{}
    \fancyfoot[R]{Constitution \space \textbf{\thepage}}
    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0.4pt}
}

%% All other Pages
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % Remove header line
\renewcommand{\footrulewidth}{0.4pt} % Add footer line

\fancyfoot[L]{QFin UWA}
\fancyfoot[C]{}
\fancyfoot[R]{Constitution \space \textbf{\thepage}}

% Subsection numbering
\titleformat{\subsection}[runin]
  {\bfseries} % Bold font
  {\thesubsection} % Include subsection number
  {1em} % Space between number and text
  {} % No additional formatting for title text

% Title
\title{\rule{\linewidth}{0.4pt}\\[0.4cm]
        Constitution \\[0.4cm]
        Quantitative Finance UWA \\[0.4cm]
        \rule{\linewidth}{0.4pt}}
\date{}

\begin{document}

\maketitle


% Name
\section{Name}
\subsection{}
The name of the club shall be Quantitative Finance UWA.


% Objectives
\section{Objectives}
\subsection{}
To encourage and facilitate:
\begin{enumerate}[label=(\alph*)]
    \item A medium through which intellectually curious students can develop practical trading, financial modeling, and quantitative research skills.
    \item To operate at the intersection of mathematics, finance, and computer science by providing students opportunities to develop back-tested algorithmic trading strategies, workshops to develop their research and scientific communication skills, and career-related events.
    \item To become and remain affiliated to Societies Council.
    \item To encourage and promote cooperation between the Club and other affiliated societies representative of the University interests.
    \item To do all such things as would appear necessary and proper for the benefit or advancement of members of the Club.
\end{enumerate}

\subsection{}
The property and income of the society shall be applied solely towards the promotion of the objectives of the club, and no part of that property may be paid or otherwise distributed, directly or indirectly, to members, except in good faith and in the promotion of those objectives.


% Ordinary Membership
\section{Ordinary Membership}
\subsection{}
Ordinary membership shall be confined to:
\begin{enumerate}[label=(\alph*)]
    \item Members of the Guild,
    \item Associates of the Guild,
    \item Honorary Life Associates of the Guild,
    \item Members of the University Senate,
    \item Members of the University Staff,
    \item Students enrolled at the University of Western Australia.
\end{enumerate}


% Associateship of the Club
\section{Associateship of the Club}
\subsection{}
The Club in General Meeting may from time to time admit persons to associateship who are, or have been:
\begin{enumerate}[label=(\alph*)]
    \item Members of the Guild,
    \item Associates of the Guild,
    \item Honorary Life Associates of the Guild,
    \item Members of the University Senate,
    \item Members of the University Staff,
    \item Students enrolled at the University of Western Australia.
    \newline
\end{enumerate}


% Subscriptions
\section{Subscriptions}
\subsection{}
The Annual subscription for ordinary membership shall be a minimum of \$4.00 (with \$2.00 Guild discount).
\newline


% Honorary Life Membership
\section{Honorary Life Memberships}
\subsection{}
The Club may in General Meeting, by two-thirds majority of those present and voting, confer Honorary Life Membership upon any member who has performed outstanding service to the Club.
\newline


% Primacy of Ordinary Members
\section{Primacy of Ordinary Members}
\subsection{}
Members other than Ordinary Members shall not:
\begin{enumerate}[label=(\alph*)]
    \item Be voting members of the Club,
    \item Nominate candidates for the offices and Committee of the Club,
    \item Become or remain office bearers of the Club,
    \item But shall otherwise have all the rights and privileges of ordinary membership.
    \newline
\end{enumerate}


% Meetings of the Club
\section{Meetings of the Club}
\subsection{}
The Club shall hold its Annual General Meeting each academic year.

\subsection{}
The Committee may at any time call a Special Meeting of the Club. The Secretary shall forthwith call a Special Meeting upon receiving a written requisition from at least 2 financial ordinary members of the Club, and such a meeting shall be held no later than ten days immediately following receipt of such a requisition.

\subsection{}
If the Secretary fails to call the meeting within that time, any of the signatories of the requisition may do so. Any business set out in the requisition shall have priority over all other business. \newline


% Provisions Governing General Meetings
\section{Provisions Governing General Meetings}
\subsection{} The Secretary shall cause written notice of any General Meeting to be posted on the Guild notice boards, or in G-News, at least seven days before the date appointed for that meeting.
\subsection{} No General Meeting may be held while a Guild General Meeting is in progress. This shall not apply where written notice of the meeting was given before written notice of the Guild General Meeting. Any such meeting being conducted in contravention thereof shall disband immediately on the order of the disciplinary officer of the Guild.
\subsection{} The quorum of General Meetings shall consist of a minimum of fifteen or two-thirds of Financial Ordinary Membership.
\subsection{} All General Meetings of the Club shall be conducted in accordance with the procedure prescribed in the Standing Rules and Orders of the Guild Council.
\newline


% Patron
\section{Patron}
\subsection{} The Club may, at the Annual General Meeting, elect a patron who shall, if they indicate their willingness to do so, hold office until the succeeding Annual General Meeting; nominations shall close at that meeting.
\newline


% Nominations
\section{Nominations}
\subsection{} Before the Annual General Meeting, the Secretary shall call for nominations for the Executive
Office Bearers and Committee of the Club.
\subsection{} Included in the same notice shall be details of the Annual General Meeting. Nominations shall close at that meeting.
\newline


% Executive Office Bearers
\section{Executive Office Bearers}
\subsection{} The Executive Office Bearers of the Club shall be elected by the Ordinary Members of the Club at the Annual General Meeting and shall consist of, in order of seniority:
\begin{enumerate} [label=(\alph*)]
    \item The President
    \item The Education Vice President
    \item The Technology Vice President
    \item The Secretary
    \item The Treasurer
\end{enumerate}

\subsection{} These members will be representatives of the appropriate Guild Sub-committee/s and Guild Meetings. 
\subsection{} Only financial Ordinary Members of the Club who are also members of the Guild shall be eligible for election as Executive Office Bearers. 
\subsection{} Election shall be conducted by optional preferential ballot for each office in the order shown above. 
\subsection{} A Candidate defeated for one office may stand for any office lower on the list. 12.6 The powers and duties of Executive Office Bearers are defined in Articles 21-24. 12.7 No Executive Office Bearer can hold more than one position simultaneously. 
\subsection{} The Committee in meeting may dismiss an Elected Office-Bearer where, in the opinion of three quarters of the members of the Committee present and voting, that Elected Office-Bearer has: 

\begin{enumerate} [label=(\alph*)]
    \item Consistently failed adequately to discharge the duties of that position; or 
    \item  Been absent from three consecutive Committee Meetings without providing a reasonable explanation; and 
    \item  Been given at least seven days‘ notice of that Committee Meeting; and \item  Been accorded the opportunity to be present and to speak at that Committee Meeting.
\end{enumerate}

\subsection{} No Executive Office Bearer can hold more than one position simultaneously.
\subsection{} The Committee in meeting may dismiss an Elected Office-Bearer where, in the opinion of
three quarters of the members of the Committee present and voting, that Elected Office-Bearer has:

\begin{enumerate}[label=(\alph*)]
    \item Consistently failed adequately to discharge the duties of that position; or
    \item Been absent from three consecutive Committee Meetings without providing a reasonable explanation; and
    \item Been given at least seven days‘ notice of that Committee Meeting; and
    \item Been accorded the opportunity to be present and to speak at that Committee Meeting.
    \newline
\end{enumerate}

% The Committee
\section{The Committee}
\subsection{} The Committee of the Club shall consist of:
\begin{enumerate}[label=(\alph*)]
    \item The Executive Office Bearers;
    \item The Ordinary Committee who shall consist of: Ordinary Committee Members and be elected by the financial Ordinary Members of the Club by optional preferential ballot of the Annual General Meeting subsequent to the election of Office Bearers.
    \item The Immediate Past President.
    \begin{enumerate}[label=(\roman*)]
        \item Only the person who held the Elected Office Bearer position of President immediately preceding the commencement of the current President‘s term shall be appointed Immediate Past President. 
        \newline
    \end{enumerate}
\end{enumerate}


% Duration of Office
\section{Duration of Office}
\subsection{} The Executive Office Bearers and the Ordinary Committee members shall remain in office until the next Annual General Meeting.
\newline


% Vacancies
\section{Vacancies}
\subsection{} If an Office Bearer resigns or ceases to hold office for any reason the remaining members of the Committee shall forthwith fill the vacancy so created by appointing thereto a member of the Committee from the Ordinary Membership, subject to review at the next General Meeting.
\newline


% Meetings
\section{Meetings}
\subsection{} The Committee shall meet at such times and places as the President shall determine.
\subsection{} The Secretary shall cause all members of the Committee to receive seven days notice before
the date fixed for the meeting together with an agenda of the business to be discussed.
\subsection{} The Secretary shall forthwith call a Special Meeting of the Committee upon receiving a
written requisition from at least two members thereof, and such a Special Meeting shall be held not
later than seven days immediately following receipt of requisition.
\subsection{} If the Secretary fails to call the meeting within that time, any one of the members signing the requisition may do so. Any business set out in the requisition shall have priority over all other business.
\newline


% Quorum and Procedure of Committee
\section{Quorum and Procedure of Committee}
\subsection{} The quorum of the Committee shall be 4 of whom at least two shall be Office Bearers.
\subsection{} All meetings of the Committee shall be conducted in accordance with the procedure prescribed
in the Standing Rules and Orders of the Guild Council.
\newline


% Power of the Committee
\section{Power of the Committee}
\subsection{} Subject to this Constitution, the Committee shall be responsible to the Club in General Meeting for giving effect to the Objectives of the Club as set out in Article 2 and elsewhere in this Constitution and for carrying on its everyday business, and without prejudice to the generality of
the foregoing, have the power to:
\subsection{} Acquire and dispose of property; dispose of monies; open banking accounts; and enter into contracts. Unless acting under a special enabling resolution of General Meeting, however, the Committee shall not borrow or raise money or incur debts or liabilities on behalf of or in the name of the Club to a greater amount than five dollars for each and every then existing financial Ordinary Member of the Club.
\subsection{} Make regulations for the orderly and proper management of the affairs of the Club, ensuring that no regulation is inconsistent or repugnant with this Constitution.
\subsection{} Make, alter or repel By-Laws and impose fines for the breach therefore. All By-Laws and any
alterations or amendment therefore shall be subject to ratification by Societies Council and Guild Council before coming into force. The maximum fine imposed may not exceed five dollars.
\newline


% Chair
\section{Chair}
\subsection{} The President shall have the right to take the Chair at any meeting of the Club or of the
Committee.
\subsection{} If the President is absent or does not wish to exercise his right at any meeting, that right
shall develop upon the Vice President.
\subsection{} In the event of absence of both the President and the Vice President, or in event of them both not wishing to exercise their right, that meeting shall elect its own Chair.
\newline 


% President
\section{President}
\subsection{} In addition to any provisions set out elsewhere in this Constitution or in any By-Laws or Regulations made hereunder, it shall be the duty of the President to: 
\begin{enumerate}[label=(\alph*)]
    \item Coordinate and supervise the work of the Executive Office Bearers, subject to the authority of the Club in General Meeting. 
    \item See that all Office-Bearers are conversant with the Constitution and their respective Duties and Responsibilities. 
    \item Generally carry out the policy of the Club. 
    \newline
\end{enumerate}


% Education Vice President
\section{Education Vice President}
\subsection{} In addition to any provisions set out elsewhere in the Constitution or in any By-Laws or Regulations made hereunder, it shall be the duty of the Education Vice President to assist the President wherever possible, as well as:
\begin{enumerate}[label=(\alph*)]
    \item Host weekly Trading Team workshops, as well as educational workshops to the general public.
    \item Coordinate and supervise the work of the Trading Team.
    \item Responsible for ensuring that Trading Team members act within the parameters of this constitution.
    \item Works in collaboration with the Treasurer to ensure responsible allocation, in line with the club conduct specified within this constitution, of funds to trading.
    \newline
\end{enumerate}


% Technology Vice President
\section{Technology Vice President}
\subsection{} In addition to any provisions set out elsewhere in the Constitution or in any By-Laws or Regulations made hereunder, it shall be the duty of the Technology Vice President to assist the President wherever possible, as well as: 
\begin{enumerate}[label=(\alph*)]
    \item Be primarily responsible for the Trading Team Project and our in-house Trading Systems.
    \item Coordinate and supervise the work of the Trading Team.
    \item Responsible for ensuring that Trading Team members act within the parameters of this constitution.
    \item Works in collaboration with the Treasurer to ensure responsible allocation, in line with the club conduct specified within this constitution, of funds to trading.
\newline
\end{enumerate}


% Secretary
\section{Secretary}
\subsection{} In addition to any provisions set out elsewhere in the Constitution or in any By-Laws or Regulations made hereunder, it shall be the duty of the Secretary: 
\begin{enumerate}[label=(\alph*)]
    \item To record all proceedings of the Club and the Committee in a Club Minute Book which they shall cause to be provided for that purpose: 
    \item To conduct and keep copies of all correspondence of the Club:
    
    \begin{enumerate}[label=(\roman*)]
        \item To supply the Secretary of the Guild before the end of the first academic semester the information required to be recorded in the Guild register of the University societies. 
        \item To notify the Secretary of the Guild within fourteen days of the alterations in the foregoing information. 
        \item To lodge with the Secretary of the Guild a copy of the Constitution and any By-Laws made under its authority. 
    \end{enumerate}
    
\item To notify the Secretary of the Guild within fourteen days from the making therefore of any alterations to this Constitution of such By-Laws. 
\item To notify the Secretary of Societies Council and Public Affairs Council of the names of the delegate and deputy delegate to Societies Council and Public Affairs Council at least four days before meetings of these respective councils in each calendar year. 
\item In the event of the Club being de-registered, to present to the Guild Secretary within thirty days a duly audited statement of the financial position of the Club together with a copy of the resolution, which may have been passed by the Club as to the disposition of its funds. 
\newline
\end{enumerate}


% Treasurer
\section{Treasurer} 
\subsection{} In addition to any provisions set out elsewhere in the Constitution or in any By-Laws or Regulations made hereunder, it shall be the duty of the Treasurer: 
\begin{enumerate}[label=(\alph*)]
    \item Keep proper books of account dealing with the property and finances of the Club and to furnish the Committee with such accounts and information relating to the finances and property of the Club as the Committee from time to time require. 
    \item Arrange and be responsible for handling of the petty cash and to render an account to each Committee member of all petty cash. 
    \item Prepare a financial statement showing all receipts and payments during their term of office, for presentation with auditors report to the Annual General Meeting. 
    \item Produce and deliver all necessary books, vouchers and other documents to the persons appointed by the Guild Finance Committee for the purpose of conducting an audit, in so far as such persons may so required. 
    \item Prepare necessary forms, and receipts for Societies Council in accordance with Semester \& O-day Grant Policies.
    \newline
\end{enumerate}


% Deposits and Withdrawal of Monies
\section{Deposits and Withdrawal of Monies}
\subsection{} All monies due and payable to the Club shall be received by the Treasurer who shall lodge them without undue delay in the Central Banking of Guild Council for the credit of the Club. 
\subsection{} Any two members of the Executive may jointly sign cheques and forms of authority for the payment of funds of the Society. 
\subsection{} Not withstanding anything contained herein, no persons shall deposit or withdraw any monies into any account that Guild Council has closed by resolution.
\newline


% Payments
\section{Payments} 
\subsection{} No payments shall be made on behalf or in the name of the Club unless it has been authorised by the Executive Office Bearers, in accordance with Article 2.2.
\newline


% Major Obligations to the Guild
\section{Major Obligations to the Guild}
\subsection{} The Club shall comply with the Regulation of the Guild, the Rules of Societies Council, and all other provisions enrolled upon the Guild Statutes book. 
\subsection{} All Office Bearers and committee members shall be jointly and severally responsible for such compliance, and shall be deemed liable in the event of noncompliance therewith. 
\newline


% Expulsion of Members
\section{Expulsion of Members}
\subsection{} The Committee may by unanimous vote request any member or associate member to resign from the Club, and in the event shall cause written notification of such request to be served upon the member concerned. 
\subsection{} Should such a request prove ineffectual after fourteen days of written notification, the Committee may serve written notice of intended expulsion of the member concerned and should they not have resigned seven days after, the Committee may by unanimous vote expel him or her from the Club; but such expulsion shall be subject to review at the next General Meeting with the member present and to be heard. 
\newline


% Availability of Constitution
\section{Availability of Constitution}
\subsection{} The Committee shall make the Constitution available on request to all Ordinary Members electronic copies of this Constitution, or 50 cents per hard copy. 
\newline


% Interpretation
\section{Interpretation}
\subsection{} Subject to any provisions enrolled upon the Guild Statutes book and to any resolution passed by Guild Council, Societies Council or Public Affairs Council, the President shall have the power to interpret the meaning of any of the provisions contained in the Constitution, but the determining decision in case of doubt shall rest with the Club in General Meeting. 
\newline


% Amendment of this Constitution
\section{Amendment of this Constitution}
\subsection{} Any two financial Ordinary Members of the Club may not less than three days before the day appointed for the next General Meeting submit to the Secretary a notice of motion signed by them proposing an alteration to this Constitution. This shall be posted on notice boards forthwith. 
\subsection{} The motion may then be considered by the Club at its next meeting and amendments that are relevant to the subject matter thereof may be moved without notice.
\subsection{}The motion of any amendment thereto shall not be deemed adopted unless it receives a two-thirds majority of the members present and voting. 
\subsection{} The motion of any amendment thereto shall not be deemed adopted unless it receives a majority of the members present and voting. 
\subsection{} The motion as adopted with any amendments shall come into force upon receiving the approval of Societies Council.

\end{document}
